%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------HEADING-----------
\begin{document}

\begin{center}
    \textbf{\Huge \scshape Alaqmar Gandhi} \\ \vspace{1pt}
    \small +1 (289) 931-0053 $|$ \href{mailto:ag22oq@brocku.ca}{\underline{ag22oq@brocku.ca}} $|$ 
    \href{https://linkedin.com/in/alaqmarg}{\underline{linkedin.com/in/alaqmarg}} $|$
    \href{https://github.com/alaqmarg}{\underline{github.com/alaqmarg}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Brock University}{Sep 2023 -- Dec 2027}
      {Bachelor of Science in Computer Science - Co-op (Honours) | GPA: 3.9}{Ontario, Canada}
    \resumeItemListStart
      \resumeItem{Programming for Big Data (NumPy, pandas)}
      \resumeItem{Data Structures and Algorithms}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
%

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Game Developer}{Mar 2025 -- Present}
      {Shiloh \& Bros}{Tennessee, USA (Remote)}
      \resumeItemListStart
        \resumeItem{Developed packages for internal \textbf{Wally} registry, reducing development time by 30\%, by leveraging reusability.}
        \resumeItem{Contributed to the development of M.O.M. HQ written in \textbf{Luau}, reaching 20k+ visits in early open beta.}
        \resumeItem{Implemented CI/CD pipelines for packages, utilised for 10+ packages, fully automating package publishing}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{May 2024 -- Feb 2025}
      {Boltable Studio}{Abu Dhabi, UAE (On-site)}
      \resumeItemListStart
        \resumeItem{Developed an \textbf{ASP .NET} API to process 2M+ monthly ad impression reports, empowering the billings' dashboard.}
        \resumeItem{Managed historical game analytic data using \textbf{MongoDB} and \textbf{JavaScript} for 449M+ game visitors.}
        \resumeItem{Containerized a full-stack \textbf{MERN} website using \textbf{Docker}, resulting in a 40\% reduction in build time.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{GitHub Actions} and integrated \textbf{Portainer} to reduce deployment times by 50\%.}
        \resumeItem{Contributed to the development of \href{https://boltablestudio.com}{\underline{boltablestudio.com}} using \textbf{React} and \textbf{Next.js}, serving 1k+ monthly visitors.}
        \resumeItem{Developed 3+ brand experiences using Roblox Studio and \textbf{Roblox Luau}, generating 120k+ USD in revenue.}
        % \resumeItem{Implemented version control workflows for Roblox experiences using \textbf{Knit, Argon and Git}, used in 12+ experiences.}
        % \resumeItem{Developed CI/CD pipelines for Roblox experiences utilizing \textbf{GitHub Actions} using the Roblox Open Cloud API, being adopted as standard infrastructure for all new experiences.}
      \resumeItemListEnd

    \resumeSubheading
      {Lua Programmer}{Sep 2023 -- Feb 2024}
      {LandVault}{London, UK (Remote)}
      \resumeItemListStart
        \resumeItem{Developed and implemented algorithms for \textbf{procedurally generated} mini-games in Roblox \textbf{Luau.}}
        \resumeItem{Developed \textbf{custom physics mechanics} to work with the Roblox game engine, reducing client compute load by 20\%.}
        \resumeItem{Managed player data within the experience utilizing \textbf{ProfileService}, capable of handling 7M+ players.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Extracurriculars}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Brock Computer Science Club} $|$ \emph{Angular (TypeScript, HTML, SCSS), Firestore, GitHub Pages}}{Oct 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a merchandise store for a static website utilizing \textbf{Stripe sessions API}, fulfilling 20+ orders.}
            \resumeItem{Contributed to the development of a static website written in \textbf{Angular}, serving 500+ CS students.}
            \resumeItem{Utilised \textbf{FireStore} to save and access administrative configuration and event information data for 100+ events.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{International Collegiate Programming Contest} $|$ \emph{Python, C++}}{Oct 2023}
      \resumeItemListStart
          \resumeItem{Competed against 159 teams in the ICPC NA East Central region, placed \textbf{top 4} universities on the Windsor site.}
          \resumeItem{Collaborated in a team of 3 and \textbf{solved 8 of 12} competitive programming problems.}
          \resumeItem{Utilised \textbf{C++} to write time efficient solutions for limited runtime problems.}
        \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{ByteNet} $|$ \emph{Luau, Networking}}{Feb 2025}
        \resumeItemListStart
          \resumeItem{Contributed to the development of \textbf{ByteNet}, an open source blazing fast Roblox networking library written in \textbf{Luau}.}
          \resumeItem{Developed a \textbf{buffered networking} library for Roblox Luau, reducing packet processing time by 75\%.}
          \resumeItem{Contributed to data \textbf{serialization} over Roblox remotes to help reduce average packet size by 79\%.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
%

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript/TypeScript, C, C++, C\#, HTML/CSS, Lua} \\
     \textbf{Frameworks}{: React, Node.js, Next.js, Angular, Knit, ASP .NET, Express.js} \\
     \textbf{Developer Tools}{: Git, Docker, Portainer, Harbor, Rojo/Argon, MongoDB, VSCode, PyCharm, IntelliJ, Wally, Moonwave} \\
     \textbf{Libraries}{: pandas, NumPy, ProfileService, ByteNet}
    }}
 \end{itemize}
%

\end{document}
